Transforming Trash as an Artistic Act

### 2015-11-09 chapter1.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721

%****************************************
% Structure of this chapter
% Section: topic and its significance
% Section: the purpose of this study
% Section: overview of chapters

% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time. Changes through the time.
% Konu hakkındaki temel bilgiler.
% Konunun ele alınan kısmı.
%

@@

Trash in every age. In other words it is part of human activity. It exists early ages of human to now. Trash is part of the early days of human production / or activity. Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human. Legs, bones etc. [TODO etymology reference, see appendix] Archaeologist find things from people throw away.

Trash in every society. Some of them called as trash the others don't.  
% TODO look introduction of revista, there is a related reference above it.

Trash is everywhere.
% Sad chair http://www.keaggy.com/chairs/sad/12/. Bu iş aslında çöpün her yerde olduğunu gösteriyor? Aslında sadece sandelye üzerinden gidiyor ama binbir çeşit sandelye.

@@

@@

@@

>>>>

%****************************************
% Structure of this chapter
% Section: topic and its significance
% Section: the purpose of this study
% Section: overview of chapters
% Section: a note on terminology

Western societies from periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible. Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them. In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated. Stages and expression of this practice is examined with my artwork in the context of art.

% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time.
% Konu hakkındaki temel bilgiler.
% Konunun ele alınan kısmı.
%

@@

Trash is global, and shared concept for all societies throughout the ages. 
\textbf{Trash in every age.} In other words it is part of human activity of every historic age. It exists early ages of human to now. Trash is part of the early days of human production / or activity. Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human. Legs, bones etc. [TODO etymology reference, see appendix] Archaeologist find things from people throw away. 
\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
% TODO look introduction of revista, there is a related reference above it.
\textbf{Trash is everywhere.}
% Sad chair http://www.keaggy.com/chairs/sad/12/. Bu iş aslında çöpün her yerde olduğunu gösteriyor? Aslında sadece sandelye üzerinden gidiyor ama binbir çeşit sandelye.

@@

There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.

Yes using non art objects in the art is introduced and opened new dimensions for the language of art. But some of them treated as sculptures from trash. Reflects our world. But it is not limited with this. It also evoke it. And offers an alternative.

% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash.

% Çöp hakkındaki genel geçer bilgileri sıralamak aslında iyi olabilir. Ya da bunun hakkındaki yanlış bilinmeyen şeyleri.

% Aslında sadece bir heykel işi olan şeylerden bahsedebilirim, ya da aslında belki de içine girip dokunabildiğin bir şey olabilir.

% Çöpe dair araştırmalar falan.

% Şöyle bir şey var, sanata non-art objelerin girmesinden bahsediyoruz ama artık orda o seviyede değiliz. O zamandan bu zamana çok şey değişti.

% Savunma.
% Yani aslında bu chapterdaki fikirler vs.'ler birer supportive yaklaşımlar. neler yapılmış onları listesi. literatür taraması. ama tabi benim işime yarayanlar.

@@

In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored. Why and how are they used by the artist? Are there any differences with the original items compared to discarded items? Has using discarded material or trash specific (or special) meaning and message? This is a work to explore the re-usage of trash in artworks (place or the role in the art practice). (and also in which scope? medium, message, life practice\ldots)

% Çöpün sanat işlerinde kullanılmasının önemi ne? Bunun karşısındaki şey nedir? Diğer alanlardaki yaklaşımlar bir şey üretemiyor mu? Bu tezin önemi ne? Birilerinin bıraktığı boşluğu doldurmak mı? Ya da benim yaptığım işin önemi ne?

% Önceki işlere değinmek gerekli. Bu alanla ilgili yapılmış. Mesela ne var. İki tane tez buldum aslında tam da bu konuyla ilgili.

% Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.

@@

% Burada da upcycling kullanıyor aslında. http://www.gwynethleech.com/cups/suspended

### 2015-11-09 chapter2.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721

%%%
%%%
%%%
% FROM Examined Life
\section{Zizek on Garbage}
(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence. In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home". He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. Draw attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from our world. However, it disappears only from the world of illusions, but still exists in reality. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. We should not forget that we are part of the ecology. We must more alienated from the nature. We must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. This part will be extended later.)

>>>>

% Bu endüstriye yaklaşım günlük kişisel kullanım eşyarından dağlar yapıyor. Hepsi birisinin aynısı, steril, vs

% COFFEE CUP / Transforming them and invite other people, reveals its process.
% FROM http://www.gwynethleech.com/public-drawing/cup-windows/statement
  \begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/Gwyneth-Leech-cup5.jpg}
      \caption[Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions Variable]{I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. For ArtPrize I am showing 1001 of my cup artworks, each representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day.}
      \label{fig:GwynethLeech_TheCup}
  \end{figure}

  \begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/Gwyneth-Leech-cup3.jpg}
      \caption[Gwyneth Leech while painting in the public]{There are different versions of it. paintings on paper coffee cups displayed as installation in public window spaces. She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many placas and date. During public drawing projects she draw with other people. and so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world.}
      \label{fig:GwynethLeech_InAction}
  \end{figure}

% Günlük alışkanlıkların, dikkaten kaçan şeylerin aslında farklı şeylere dönüşmesini görüyoruz.

% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
  \begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/rubysilvious-teabag-Day237.jpg}
      \caption[Ruby Silvious, 363 Days of Tea, Day 237, 2015, Mixed media on upcycled paper tea bags, Dimensions Variable]{In the beginning of this year, visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.}
      \label{fig:RubySilvious_TeaBag}
  \end{figure}

% Potraits of Global Mass culture from Chris Jordan. In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.”

% Bu adam çok güzel bir şekilde küresel tüketimi ve onun sonuçlarını anlatıyor.

% He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.

% HAKAN GÜRSU
% Buraya aslında bir de Hakan Gürsu koymak gerekli olabilir. Yani aslında kendisi pek de sanatla ilgili bir laf etmiyor. Ama aslında tükettiğimiz onlarca şeye karşı bir tavır yaklaşım sergiliyor. Bu yüzden theory kısmında yer alabilir. Bu çöpün içinde boğulacağımızdan bahsediyor. Onu dönüştürmek gerekliliğinden yeteneğinden bahsediyor.

% Chris jordan hem bir gerçeği açığa çıkarıyor. 
% Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor. Bize konuya farklı bir açıdan bakmaya davet ediyor.

% TEZ STATEMENT.
% Ya gerçekten çöpü dönüştürüyorlar ya da çöpe dair düşünceleri dönüştürüyorlar, ve bunu ele alırken aslında heykel, kolaj, fotoğraf gibi şeylerden yararlanıyorlar ama aslında ortaya koydukları şey bir sanatsal eylem. veya bunu sanatsal eylem bağlamında ele alabiliriz.

% Aslında şöyle bir şey var mustafa, aslında sanatçının yaptığı şey ürünlerinden çok tekrar ve devamlı olarak eyleme geçirdiği yaklaşımı. Çöpün de bu tekrar eden yapısı buna uyum sağlıyor. Çünkü zaten hatayın sürekli bir parçası. Aslında bunun için şart olmasada destekleyici olduğu söylenebilir.

% Sanat işleri
% Her çöpünü fotoğraflayan adam.

% Tracy emin mesela. Yani aslında bir şekilde bir yandan aslında teoriye mi değiniyorum yoksa sanatçıların işlerine mi değiniyorum, bunların teorideki karşılıklarını mı buluyorum emin olamadım. Bunların ikisi paslaşarak ilerliyor aslında. Aslında çöplerin bize ait çok şeyler söylediğini ünlülerin çöplerini karıştıran yaklaşım ortaya çıkarıyor. Bu işde bununla ilgili aslında.

% Sanatçıların işlerine bir de bu güzel bakarsak ne görürüz.

%%%
%%%
%%%
% FROM Examined Life
\section{Zizek's Approach to Garbage}
(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence. In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home". He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. Draw attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from our world. However, it disappears only from the world of illusions, but still exists in reality. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. We should not forget that we are part of the ecology. We must more alienated from the nature. We must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. This part will be extended later.)

% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
  \begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/ChrisJordan-Albatross.jpg}
      \caption[Chris Jordan, Albatross at Midway Atoll Refuge, 2009]{The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.}
      \label{fig:ChrisJordan_Albatross}
  \end{figure}

Using spare narration and stunning imagery, Chris Jordan's feature film MIDWAY explores the plight of Laysan albatross plagued by the ingestion of our plastic trash. Both elegy and warning, the film explores the interconnectedness of species, with the albatross on Midway as a mirror of our humanity.

Even if garbage leave outs our life, we do not care about the results of it. And it is captured by the works of Chris Jordan.In this photo series it captures

% Effect of plastic on wildlife in Antartica.
% Her ne kadar biz çöpü attıktan bizim hayatımızdan çıksa da yok olmuyor. Sadece başka bir yerlere gidiyor. Mesela kuşların midelerine. Chris Jordan'ının imageları bunu çok da güzel açığa çıkartıyor. Bizim çöpleriminde habersiz hayvanlar bunları yiyorlar. Bir yandan ürettiğimiz ürünler ile kaynakları tüketirken bir diğer yandan ise artıklarımız diğer yaşanları tüketiyor. Dikkat çekmek istediğim nokta aslında ekolojik hassasiyetlerden çok aslında elimizde avucumuzda ne varsa onları tüketiyor olmamız. Karşı durduğum nokta ise tam olarak burası.

### 2015-11-09 chapter4.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721

@@

>>>>

% TODO
% Felix Gonzales Torres'in untitled işi benim yapmaya çalıştığım ile ilgili.

@@

% Eğer bir artistic actten bahsediyorsak sadece bunun ürünle değil, üretimi ve insanların dahil olmasıyla desteklenebilir. Zaten toplama sürecinde bunu insanlarla ilişki kurarak yapıyorum. O insanlarda diğerleriyle konuşarak yapıyorlar.

% At this stage it is claimed that the process of transformation of trash can be treated as artistic act. In the production of notebooks people collected papers from different places and location. During the collection phase they also collect them from other people. In other words there is human communication during this process.

Actually (It is questioned that) working with trash dictates a life practice and, it is a convergence of behavioral patterns (attitudes toward to trash) and art making. The process effects one's life and lifestyle. (But what type of interaction between life and art making process?) (This claim is the main driving force of my artwork which is part of a thesis.) The purpose is not to build a thing that is produced from discarded material to watch it from a distance. The important thing is to interact with it. Because it is already discarded (disgusting, abject, unattractive etc.) and general behavior avoid from it, this work must change it. It must call the viewer to interact with it.

% Ersan hoca uzak seyretmek yerine etkileşime geçilmesini auranın kırılması olarak bakıyor. Performatif olması veya bir act olması zaten bunu kıran bir şey olabilir. Sanatsal eylem, performans kavramlarını araştırmak gerekli. Uzaktan seyredip hayranlık duymak yerine ilişkiye geçilen bir hale getirmek çöpü. Amaç bu aslında. Çöpü tekrar tanımak, onunla barışmak, onunla yaşamak. İşte bu yüzden bir eylem olabilir. Ya da yaşam pratiği.

% Olay sadece böyle çöpten bir şeyler yapıp insanların seyretmesi değil, mühim olan onunla iletişime, ilişkeye geçmek. Yani zaten uzak durulan bir şey, onlardan bir şey üretildiğinde izleyici gene uzağında duruyorsa ne anlamı kaldı ki? İnsanların bu işin aşamalarının bir parçası olmalılar.

With the help of art (and artistic practices) discarded things can find a place in the society. (By the help of artistic approach things can be gain new values and meaning even if they are discarded and excluded from daily life (or society). The relationship between value creation and artistic practice examined through the artworks that uses trash as medium.)

% Using trash can not only understand in ecological perceptions, it also have powerful political claims. Or it should be examined in deeper levels beyond collage and assemblage, the medium itself has different meanings.

% SEEING IT AS A RESOURCE.
Junk(or trash) can be seen as a new resource that is fertile to new meanings, creations and aesthetics. Ignored and discarded nature of garbage when rethought becomes fertile resource. Trash as a resource (as an artistic material). (City as a resource. Seeing the discarded items as a resource. Many artist approach to trash as resource. It is a shared approach. Some of them collect city discard, some of them tea cups, tea bags, discarded papers.)

% Çöpü tekrar ele alıp bir şeyler üretmek, onu tekrar yaşamımıza sokmak yeni alternatifler sunacaktır.

Do she/he want to take back (or revisit) the trash once thrown away? People do not want to think of what they throw away. Turning them to a things that worth to look again. How do artists reflect garbage and what are their tactics? What is the thing that add value to trash and what is the role of art in that?

With the help of art discarded things ---in the scope of thesis in particular paper trash--- can be transformed beyond the other industrial (or technological) methods. In other words autistics practices generates applies different methods.
